Optimal strategies in mental rotation tasks

### 2013-05-13 man/final-project.tex
Add a bit about BQ results (not done)

>>>>

The rotations computed by the nonparametric model are the most
strongly correlated with the true rotations, albeit negatively so
($\rho=-0.60$). In general, the nonparametric model rotates much more
than should be necessary; this is because the Bayesian quadrature
estimate of $Z$ is too large to accept either hypothesis until a
significant portion of the rotations have been sampled.
